Efficient Feasibility Checking Algorithm of Photovoltaic Array Reconfiguration

### 2019-11-28 Journal-Photovoltaic/manuscript.tex
Zhao push @ 2019-11-28 16-29-10

In order to improve PV system power generation efficiency and protect PV cells from damage, an efficient and effectively PV system manage method is worth to investigate.

>>>>

In order to improve PV system power generation efficiency and protect PV cells from damage, an efficient and effectively PV system manage method is worth to investigate.
The key to improve power generation efficiency is to maintain maximum output power.
Thus, different maximum power point tracking (MPPT) algorithms have been proposed in this regard.
In different MPPT algorithms, P\&O\cite{kasa2000maximum,jain2004new,chomsuwan2002photovoltaic,wasynezuk1983dynamic}and hill climbing\cite{koutroulis2001development,teulings1993new,xiao2004modified} methods received many attention due to its low complexity and implement cost.
Hill climbing and P\&O methods are different ways to implement the same fundamental method.
Using the approximate linear relationship between $V_{OC}$,$I_{SC}$ and $V_{MPP}$, $I_{MPP}$, fractional voltage-based and current-based MPPT are popular due to their linear dependency of PV panel characteristic and irradiance level\cite{Liu2016,kobayashi2004novel,bekker2004finding,mutoh2002prediction,noguchi2001short}.
However, under abnormal working condition such as partial shading, it is very hard for conventional MPPT algorithms to find global maximum power point.
Meanwhile, without any PV module level improvement, it is impossible to protect PV panel against hot-spotting\cite{Olalla2018,ghanbari2016permanent}.

Another attractive direction to improve PV system efficiency under different working condition is PV reconfiguration.
